---
title: "homework1_xw2598"
author: "Xinyao WU"
date: "2018/9/18"
output:
  html_document:
    toc: true
    toc_float: true
---
# *problem 1* 
##code chunk 1

_Create a data frame comprised of:_

_A random sample of size 10 from a uniform[0, 5] distribution._

_A logical vector indicating whether elements of the sample are greater than 2._

_A (length-10) character vector._

_A (length-10) factor vector._
```{r chunk1}
library(tidyverse)
dt_frame = tibble(
  random_sample = runif(10,0,5) ,
  logical_vector = random_sample > 2 ,
  ch_vector = c("a","b","c","d","e","f","g","h","i","j") ,
  factor_vector = as.factor(ch_vector) 
)
dt_frame = as.data.frame(dt_frame)
head(dt_frame)

```
##The mean of each variable in the dataframe

The mean of **random sample** is `r mean(dt_frame$random_sample)`

The mean of the **logical vector** is `r mean(dt_frame$logical_vector)`

The mean of the **character vector** is `r mean(dt_frame$ch_vector)`

The mean of the **list of factor vector** is `r mean(dt_frame$factor_vector)`

**Explanation:**The random sample and logical vector worked while character vector and factor vector didn`t work. According to the useage of mean(), the elements of the vector should be umeric/logical vectors and date, date-time and time interval objects.

## code chunk 2 

```{r chunk2, results='hide',warning=FALSE}

chr_to_num = as.numeric(dt_frame$ch_vector) 
chr_to_factor = as.factor(dt_frame$ch_vector) 

factor_to_chr = as.character(dt_frame$factor_vector) 
factor_to_num = as.numeric(dt_frame$factor_vector) 

logic_to_num = as.numeric(dt_frame$logical_vector) 

```
**Explanation：**This shows the variables cannot be converted from character to numberic. Except that, some other kinds of conversions(factor to numberic to character,logic to numberic, character to factor ) can be realized successfully.


# *problem 2 *
##code chunk 3
*Create a data frame comprised of:*

*x: a random sample of size 1000 from a standard Normal distribution.*

*y: a random sample of size 1000 from a standard Normal distribution.*

*A logical vector indicating whether the x + y > 0.*

*A numeric vector created by coercing the above logical vector.*

*A factor vector created by coercing the above logical vector.*

```{r chunk3}
library(tidyverse)
dt_frame2 = tibble(
  x = rnorm(1000, mean = 0, sd = 1) , 
  y = rnorm(1000, mean = 0, sd = 1) ,
  vc_logic = x + y > 0 ,
  vc_num = as.numeric(vc_logic) ,
  vc_factor = as.factor(vc_logic)
)
dt_frame2 = as.data.frame(dt_frame2)
head(dt_frame2)

```
The size of the dataset is `r nrow(dt_frame2)` .

The mean of x is `r mean(dt_frame2$x)` and the median of x is `r median(dt_frame2$x)` .

The proportion of cases for which the logical vector is TRUE is `r  round(sum(dt_frame2$vc_num)/1000,3)`.

##scatterplot

```{r}
ggplot(dt_frame2, mapping = aes(x,y))+geom_point(data = dt_frame2, aes(x,y), col = ifelse(dt_frame2$vc_logic,"red","blue"), size =1 ) +labs(title = "scatterplot of y vs x ")
ggsave("scatterplot_of_x_vs_y_colored_logic.pdf")

ggplot(dt_frame2, mapping = aes(x,y))+geom_point(data = dt_frame2, aes(x,y), col = ifelse(dt_frame2$vc_num,"blue","green"), size =1 ) +labs(title = "scatterplot of y vs x ")

ggplot(dt_frame2, mapping = aes(x,y))+geom_point(data = dt_frame2, aes(x,y), col = ifelse(dt_frame2$vc_factor == "TRUE","purple","violet"), size =1 ) +labs(title = "scatterplot of y vs x ")

```



