---
title: "homework1_xw2598"
author: "Xinyao WU"
date: "2018/9/18"
output:
  html_document:
    toc: true
    toc_float: true
---
# *problem 1* 
## code chunk 1
Create a data frame comprised of:

A random sample of size 10 from a uniform[0, 5] distribution

A logical vector indicating whether elements of the sample are greater than 2

A (length-10) character vector

A (length-10) factor vector

```{r chunk1}
library(tidyverse)
dt_frame = tibble(
  random_sample = runif(10,0,5) ,
  logical_vector = random_sample > 2 ,
  ch_vector = c("a","b","c","d","e","f","g","h","i","j") ,
  factor_vector = as.factor(ch_vector) 
)
dt_frame = as.data.frame(dt_frame)
dt_frame

```
##The mean of each variable in the dataframe

The mean of random sample is `r mean(dt_frame$random_sample)`

The mean of the  logical vector is `r mean(dt_frame$logical_vector)`

The mean of the character vector is `r mean(dt_frame$ch_vector)`

The mean of the list of factor vector is `r mean(dt_frame$factor_vector)`

The random sample and logical vector worked while character vector and factor vector didn`t work. According to the useage of mean(), the elements of the vector should be umeric/logical vectors and date, date-time and time interval objects.

## code chunk 2 

```{r chunk2, results='hide'}

chr_to_num = as.numeric(dt_frame$ch_vector) 
chr_to_factor = as.factor(dt_frame$ch_vector) 

factor_to_chr = as.character(dt_frame$factor_vector) 
factor_to_num = as.numeric(dt_frame$factor_vector) 

logic_to_num = as.numeric(dt_frame$logical_vector) 

```
This shows the variables cannot be converted from character to numberic. Except that, other kinds of conversion can be realized.




# *problem 2 *




